Modelling the Yelp Rating of Restaurants: Disparity of Rating Between Restaurant Cuisines and Prices

### 2024-04-19 paper/paper.qmd
style files

We used the programming language R [@citeR], along with packages `tidyverse` [@tidyverse], `rstanarm` [@rstanarm], `jsonlite` [@jsonlite], `arrow` [@arrow], `modelsummary` [@modelsummary], `kableExtra` [@kableExtra], `here` [@here], `leaflet` [@leaflet], `htmlwidgets` [@htmlwidgets].

@@

data |>
  ggplot(aes(x = rating)) +
  geom_histogram(binwidth = 0.25, fill = "grey", color = "black") +
  labs(title = "Distribution of Star Ratings",
       x = "Stars",
       y = "Frequency") +
  theme_minimal()
```

@@

# Plot the relationship between cuisine and price range with normalized counts
data_normalized |>
  ggplot(aes(x = cuisine, y = normalized_count, fill = factor(price))) +
  geom_bar(stat = "identity") +
  labs(x = "Cuisine",
       y = "Percentage",
       fill = "Price Range") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

@@

# Plot number of restaurants vs average rating
ggplot(cuisine_summary, aes(x = num_restaurants, y = avg_rating)) +
  geom_point() +
  geom_text(aes(label=cuisine), nudge_y = 0.02, size = 3, angle = 25) +
  labs(x = "Number of Restaurants", y = "Average Rating") +
  theme_minimal()
```

@@

cuisine_summary <- data %>%
  group_by(cuisine) %>%
  summarize(avg_price = mean(as.numeric(factor(price), ordered = TRUE)),
            avg_rating = mean(rating))

# Plot
ggplot(cuisine_summary, aes(x = avg_price, y = avg_rating, label = cuisine)) +
  geom_point() +
  geom_text(aes(label = cuisine), nudge_x = 0.05, nudge_y = 0.05, size = 3, angle = 45, hjust = 1) +  # Add text labels with a slight nudge and angle
  labs(x = "Average Price", y = "Average Rating",) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

@@

@@

pp_plot <- pp_check(model) +
  theme_classic() +
  theme(legend.position = "bottom")
pp_plot

```

@@

plot(model, "trace") +
    theme_minimal() +
    theme(legend.position = "bottom")

```

@@

plot(model, "rhat") +
  theme_minimal() +
  theme(legend.position = "bottom")

```

>>>>

We used the programming language R [@citeR], along with packages `tidyverse` [@tidyverse], `rstanarm` [@rstanarm], `jsonlite` [@jsonlite], `arrow` [@arrow], `modelsummary` [@modelsummary], `kableExtra` [@kableExtra], `here` [@here], `leaflet` [@leaflet], `htmlwidgets` [@htmlwidgets], and `styler` [@styler].

@@

data |>
  ggplot(aes(x = rating)) +
  geom_histogram(binwidth = 0.25, fill = "grey", color = "black") +
  labs(
    title = "Distribution of Star Ratings",
    x = "Stars",
    y = "Frequency"
  ) +
  theme_minimal()
```

@@

# Plot the relationship between cuisine and price range with normalized counts
data_normalized |>
  ggplot(aes(x = cuisine, y = normalized_count, fill = factor(price))) +
  geom_bar(stat = "identity") +
  labs(
    x = "Cuisine",
    y = "Percentage",
    fill = "Price Range"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

@@

# Plot number of restaurants vs average rating
ggplot(cuisine_summary, aes(x = num_restaurants, y = avg_rating)) +
  geom_point() +
  geom_text(aes(label = cuisine), nudge_y = 0.02, size = 3, angle = 25) +
  labs(x = "Number of Restaurants", y = "Average Rating") +
  theme_minimal()
```

@@

cuisine_summary <- data %>%
  group_by(cuisine) %>%
  summarize(
    avg_price = mean(as.numeric(factor(price), ordered = TRUE)),
    avg_rating = mean(rating)
  )

# Plot
ggplot(cuisine_summary, aes(x = avg_price, y = avg_rating, label = cuisine)) +
  geom_point() +
  geom_text(aes(label = cuisine), nudge_x = 0.05, nudge_y = 0.05, size = 3, angle = 45, hjust = 1) + # Add text labels with a slight nudge and angle
  labs(x = "Average Price", y = "Average Rating", ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

@@

Be wary of lag, there are tens of thousands of datapoints being plotted, and it may lag on machines that are not fast.

The raw dataset map is here: [https://alexsohn1126.github.io/yelp-analysis/other/map/rawmap.html](https://alexsohn1126.github.io/yelp-analysis/other/map/rawmap.html)

As you can see, there are no datapoints near Toronto, Montreal, or Calgary like the documentation has stated.

The cleaned dataset map here: [https://alexsohn1126.github.io/yelp-analysis/other/map/map.html](https://alexsohn1126.github.io/yelp-analysis/other/map/map.html)

The datapoints are colored by their price ranges. Clicking on each datapoint will show it's name, rating, cuisine, and price.

@@

pp_plot <- pp_check(model) +
  theme_classic() +
  theme(legend.position = "bottom")
pp_plot
```

@@

plot(model, "trace") +
  theme_minimal() +
  theme(legend.position = "bottom")
```

@@

plot(model, "rhat") +
  theme_minimal() +
  theme(legend.position = "bottom")
```
